Cloud structure of planetary mass companion AB Pic-b

### 2015-05-09 summary/ABPIC-PAPER/msv1.tex
you have to work on 2m1207

We performed aperture photometry using images processed with above
procedures.  Centroids of PSF of AB Pic b was located by 2 dimensional
Gaussian fit with IDL routine \texttt{mpfit2dpeak}
\citep{Markwardt2009}. Then aperture photometry was calculated using
\texttt{aper} with aperture radius of 3 pixels. Aperture size is
determined by taking into account both reducing noise level as well as
excluding bad pixels.

>>>>

We performed aperture photometry using images processed with above
procedures.  Centroids of PSFs of AB Pic b were located by 2 dimensional
Gaussian fit with IDL routine \texttt{mpfit2dpeak}
\citep{Markwardt2009}. Then aperture photometry was calculated using
\texttt{aper} with aperture radius of 3 pixels. Aperture size is
determined by taking into account both minimizing noise level as well as
excluding bad pixels.
